---
title: "R Notebook"
output: html_notebook
---

## Objective  
In this project we will deal with exploratory analysis, where the objective is to understand how the data is distributed and generate insight for future decision-making, this analysis aims to explore as much as possible the data in a simple, intuitive and informative way. The data used in this project contains information only from 1980 to 2016.

## About Dataset
This dataset contains a list of video games with sales greater than 100,000 copies.It includes various fields related to the games and their platform, also this dataset mainly includes the 
sales of the countries and regions around the world.

Columns :

* Name - The names of games 
* Platform - Gaming device used for playing
* Year - Year of the game release
* Genre - Genre of the game 
* Publisher - Publisher name 
* NA_Sales - North America Sales (in millions)
* EU_Sales - Europe Sales (in millions)
* JP_Sales - Japan Sales (in millions)
* Other_Sales - Other countries sales (in millions)
* Global_Sales - Sales over the world (in millions)

```{r, warning = FALSE,echo = FALSE}
library(hrbrthemes)
library(gganimate)
library(gapminder)
library(babynames)
library(ggthemes)
library(cowplot)
library(ggplot2)

# Data Manipulation
library(tidyverse)
library(DT)

# Statistics
library(DescTools)

```
```{r, warning = FALSE,echo = FALSE}
data = read_csv("G:\\R\\My Projects\\Video Games Sales Analysis\\vgsales.csv\\vgsales.csv")
 
# removing the rank column from dataframe
data$Rank = NULL

```

```{r, warning = FALSE,echo = FALSE}
# selecting the data according to the interest of this study 
#removing the data where year is nan and years till 2016

data = data[(data$Year != "N/A" & data$Year != "2017" & data$Year != "2020"),]
data$Year = factor(data$Year)
```

```{r, warning = FALSE,echo = FALSE}
datatable(head(data))
```


```{r}
summary(data)
```
## These are the most 10 frequent years where sales were high.
```{r, warning = FALSE,echo = FALSE}
# suppressWarnings( as.numeric(c('0', '1', '2', 'three')) )
freq_year = data.frame(cbind(Frequency = table(data$Year)
                             ,Percent = prop.table(table(data$Year))*100))

freq_year = freq_year[order(freq_year$Frequency,decreasing = TRUE),]

df = head(freq_year,10)                # most frequent years

# The 10 most frequent years
a = ggplot(data = df,mapping = aes(x = row.names(df),y =Frequency))+
  geom_bar(stat = "identity",mapping = aes(fill = row.names(df),color = row.names(df)),
           alpha = 0.7,size = 1.1) +
  geom_label(mapping = aes(label = Frequency),fill = "#FFC0CB",size = 4,color = "white") +
  labs(x = "Years",y = "Frequency")+
  theme_ipsum()+
  theme(legend.position="none")

a
```



## These are the least 10 years where sales were low.
```{r, warning = FALSE,echo = FALSE}
df_1 = tail(freq_year,10)

#The 10 least frequent years
b = ggplot(data = df_1,mapping = aes(x = row.names(df_1),y = Frequency )) +
  geom_bar(stat = "identity",mapping = aes(color = row.names(df),fill = row.names(df)),
           alpha = 0.7,size = 1.5)+
  geom_label(mapping = aes(label = Frequency),fill = "#FFC0CB",size = 4,color = "white")+
  labs(x = "Years",y = "Frequency")+
  theme_ipsum()+
  theme(legend.position="none")
b
```
# North American Sales Histogram (in millions)
```{r,warning = FALSE,echo = FALSE}
q = ggplot(data = data,mapping = aes(x = NA_Sales))+
  geom_histogram(bins = 80,fill = "blue",color = "cyan")+
  labs(x = "Sales in North America (in millions)",y = "Frequency")+
  theme_minimal()

q
```

## North American Sales < 2 millions
```{r,warning = FALSE,echo=FALSE}

df_3 = data[data$NA_Sales <2,]  
w = ggplot(data = df_3,mapping = aes(x = NA_Sales))+
  geom_histogram(bins = 80,fill = "red",color = "yellow")+
  labs(x = "Sales in North America (in millions)",y = "Frequency")+
  theme_minimal()

w
```
## Europe Sales Histogram (in millions)
```{r,warning = FALSE,echo=FALSE}

z = ggplot(data = data,mapping = aes(x = EU_Sales))+
  geom_histogram(bins = 80,fill = "green",color = "black")+
  labs(x = "Sales in Europe (in millions)",y = "Frequency")+
  theme_minimal()
z
```
## Europe Sales < 2 millions
```{r,warning = FALSE,echo=FALSE}
data_EU2 = data[(data$EU_Sales<2),]
x = ggplot(data = data_EU2,mapping = aes(x = EU_Sales))+
  geom_histogram(bins = 80,fill = "grey",color = "black")+
  labs(x = "Sales in Europe (in millions)",y = "Frequency")+
  theme_minimal()
x
```
## Frequency Distribution of Games 
### Need for Speed:Most Wanted is most frequently distributed game among the whole world
```{r,warning = FALSE,echo=FALSE}
games_perc = data.frame(cbind(Frequency = table(data$Name),
                              Percent = prop.table(table(data$Name)) * 100))
games_perc = games_perc[order(games_perc$Frequency,decreasing = T),]
games_perc = head(games_perc,5)

# games_perc
m = ggplot(data = games_perc,mapping = aes(x = Frequency,y = row.names(games_perc)))+
  geom_segment(aes(xend=0, yend=row.names(games_perc),color =row.names(games_perc)),
               size = 2.5, alpha = .5)+
  geom_point(mapping = aes(fill = row.names(games_perc),color = row.names(games_perc)),size = 3.5)+
  theme(legend.position = "none")

n = ggplot(data = games_perc,mapping = aes(x = row.names(games_perc),y = Frequency ))+
  geom_segment(aes(xend=row.names(games_perc), yend=0,color =row.names(games_perc)),
               size = 2.5, alpha = .5)+
  geom_point(mapping = aes(fill = row.names(games_perc),color = row.names(games_perc)),size = 3.5)+
  labs(x = "Games")+
  theme(legend.position = "none")

plot_grid(m,n+coord_polar(),nrow = 1,ncol = 2)

```
## Frequency distribution of Gaming Platform
### PS2(PlayStation) and DS(Dual Screen) are the most used gaming devices among the world 
```{r,warning = FALSE,echo = FALSE}
# Gaming Platform
gaming_platform = data.frame(cbind(Frequency = table(data$Platform),
                                   Percent = prop.table(table(data$Platform))*100))
gaming_platform = gaming_platform[order(gaming_platform$Frequency,decreasing = T),]

gaming_platform = head(gaming_platform,7)
               
c = ggplot(data = gaming_platform,mapping = aes(x = Frequency,y = row.names(gaming_platform)))+
  geom_bar(stat = "identity",mapping = aes(fill = row.names(gaming_platform)),alpha = 0.5
           ,size = 0.5,color = "black")+
  geom_label(mapping = aes(label = Frequency),fill = "#D3D3D3",color = "black")+
  labs(x = "Frequency",y = "Gaming Platform")+
  theme(legend.position = "none")

v = ggplot(data = gaming_platform,mapping = aes(x = row.names(gaming_platform),y = Frequency))+
  geom_bar(stat = "identity",mapping = aes(fill = row.names(gaming_platform)),alpha = 0.5
           ,size = 0.5,color = "black")+
  labs(x = "Gaming Platform")+
  coord_flip()+
  theme(legend.position = "none")
plot_grid(c,v+coord_polar(),nrow = 1,ncol = 2)
```
## Frequency distribution of Genre
### Here, we can say that Action and Sports are the most played Genre in the world.
```{r,warning = FALSE,echo = FALSE}
### Genre
freq_genre = data.frame(cbind(Frequency = table(data$Genre)
                              ,Percent = prop.table(table(data$Genre))*100))
freq_genre = freq_genre[order(freq_genre$Frequency,decreasing = TRUE),]

ggplot(data = freq_genre,mapping = aes(x = row.names(freq_genre),y = Frequency))+
  geom_bar(stat = "identity",mapping = aes(fill = row.names(freq_genre)),color ="black",alpha = 0.4,size = 0.5)+
  labs(x = "Genre",y = "Frequency" )+
  geom_label(aes(label = Frequency))+
  theme(legend.position = "none")

```
## Frequency distribution of Publisher
### EA Sports is the most leading publisher of games in the world.
```{r,warning = FALSE,echo = FALSE}
freq_publisher = data.frame(cbind(Frequency = table(data$Publisher)
                            ,Percent = prop.table(table(data$Publisher))*100))
freq_publisher = freq_publisher[order(freq_publisher$Frequency,decreasing = TRUE),]
freq_publisher = head(freq_publisher,10)

ggplot(data = freq_publisher,mapping = aes(x = Frequency,y = row.names(freq_publisher)))+
  geom_line(group = 1,size = 1,color = "blue",linetype = "dashed")+
  geom_label(aes(label = Frequency,fill = row.names(freq_publisher)),color = "black",size =3)+
  labs(y = "Publishers")+
  theme(legend.position = "none")
```
## Measure of Central Tendency
### Mean of the Sales of Games 
```{r, warning = FALSE,echo = FALSE}
mean_games = data.frame(Mean = c(mean(data$NA_Sales),mean(data$EU_Sales),mean(data$JP_Sales),
                          mean(data$Other_Sales),mean(data$Global_Sales)))
row.names(mean_games) = c("NA_Sales","EU_Sales","JP_Sales","Other_Sales","Global_Sales")
mean_games

b = ggplot(data = mean_games,mapping = aes(x = Mean,y = row.names(mean_games)))+
  geom_line(group = 1,linetype = "dashed",color = "black",size = 0.8)+
  geom_point(mapping = aes(x = Mean,color = row.names(mean_games)),size = 3)+
  labs(x = "Mean",y = "Games")+
  theme(legend.position = "none")

a =ggplot(data = mean_games,mapping = aes(x = Mean,y = row.names(mean_games)))+
  geom_line(group = 1,linetype = "dashed",color = "black",size = 0.8)+
  geom_point(mapping = aes(x = Mean,color = row.names(mean_games)),size = 3)+
  labs(x = "Mean",y = "Games")+
  theme(legend.position = "none")

plot_grid(b,a+coord_polar(),nrow = 1,ncol = 2)
```
### Median of the Sales of Games
```{r, warning = FALSE,echo = FALSE}
median_games = data.frame(Median = c(median(data$NA_Sales),median(data$EU_Sales),median(data$JP_Sales),
                                     median(data$Other_Sales),median(data$Global_Sales)))
row.names(median_games) = c("NA_Sales","EU_Sales","JP_Sales","Other_Sales","Global_Sales")

median_games

```

### Mode
```{r, warning = FALSE,echo = FALSE}
mode = function(x){
  
  freq = table(x)
  return(names(freq)[freq == max(freq)])
  
}
mode_games = data.frame(Mode = c(mode(data$NA_Sales),mode(data$EU_Sales),mode(data$JP_Sales),
                                 mode(data$Other_Sales),mode(data$Global_Sales)))
row.names(mode_games) = c("NA_Sales","EU_Sales","JP_Sales","Other_Sales","Global_Sales")
mode_games
```

### All Measures of Central Tendancy together
```{r, warning = FALSE,echo = FALSE}
central_tendency = cbind(mean_games,median_games,mode_games)
central_tendency
```
## Percentile of all the Sales 
```{r, warning = FALSE,echo = FALSE}
percentile = c()
for (i in 1:99){
  percentile = c(percentile,i/100)
}

data_percentiles = data.frame(cbind(NA_Sales =quantile(data$NA_Sales,percentile),
                                    EU_Sales =quantile(data$EU_Sales,percentile),
                                    JP_Sales =quantile(data$JP_Sales,percentile),
                                    Other_Sales =quantile(data$Other_Sales,percentile),
                                    Global_Sales =quantile(data$Global_Sales,percentile)))

# filtering a dataframe by row names 
req_percentiles = c("25%","50%","75%","99%")
percentiles = data_percentiles[rownames(data_percentiles) %in% req_percentiles,]
percentiles
```
## Absolute Mean Deviation of all Sales 
```{r, warning = FALSE,echo = FALSE}
data_amd = data.frame(ADM = c(MeanAD(data$NA_Sales),MeanAD(data$EU_Sales),MeanAD(data$JP_Sales)
                              ,MeanAD(data$Other_Sales),MeanAD(data$Global_Sales)))
row.names(data_amd) = c("NA_Sales",'EU_Sales',"JP_Sales","Other_Sales","Global_Sales")
data_amd
```
## Variance among all the Sales
```{r, warning = FALSE,echo = FALSE}
data_var = data.frame(Variance = c(var(data$NA_Sales),var(data$EU_Sales),var(data$JP_Sales)
                              ,var(data$Other_Sales),var(data$Global_Sales)))
row.names(data_var) = c("NA_Sales",'EU_Sales',"JP_Sales","Other_Sales","Global_Sales")
data_var
```
## Standard Deviation among the Sales 
```{r, warning = FALSE,echo = FALSE}
data_sd = data.frame(SDeviation = c(sqrt(var(data$NA_Sales)),sqrt(var(data$EU_Sales)),sqrt(var(data$JP_Sales))
                                   ,sqrt(var(data$Other_Sales)),sqrt(var(data$Global_Sales))))
row.names(data_sd) = c("NA_Sales",'EU_Sales',"JP_Sales","Other_Sales","Global_Sales")
data_sd
```
## Measures of Dispersion all together
```{r, warning = FALSE,echo = FALSE}
Dispersion = cbind(data_amd,data_var,data_sd)
Dispersion

ggplot(data = Dispersion)+
  geom_bar(stat = "identity",mapping = aes(x = row.names(Dispersion),y = Variance,fill = "Variance")
           ,size = 1,alpha = 0.8,color = "blue")+
  geom_bar(stat = "identity",mapping = aes(x = row.names(Dispersion),y = ADM,fill = "ADM")
           ,size = 1,alpha = 0.5,color = "red")+
  geom_bar(stat = "identity",mapping = aes(x = row.names(Dispersion),y = SDeviation,fill = "SDeviation")
           ,size = 1,alpha = 0.4,color = "green")+
  xlab("")+ylab("")+
  theme(legend.position = "bottom")
```
# Explorartory Data Analysis

### Top North America sales of games
#### We can say that Wii Sports is the most sold game in the North America
```{r, warning = FALSE,echo = FALSE}
top_nasales = aggregate(list(NA_Sales = data$NA_Sales),list(Name = data$Name),FUN = sum)
top_nasales = top_nasales[order(top_nasales$NA_Sales,decreasing = TRUE),]
top_nasales = head(top_nasales,10)
top_nasales

a = ggplot(data = top_nasales, mapping = aes(x = Name, y = NA_Sales)) +
  geom_bar(stat = "identity", mapping = aes(fill = Name, color = Name), size = 1.1, alpha = .7) +
  geom_label(mapping = aes(label = NA_Sales), size =4) +
  xlab("") +
  ylab("Sales in North America (in millions)") +
  ggtitle("The 10 best selling games in North America")+
  scale_x_discrete(guide = guide_axis(n.dodge=2))+
  theme(legend.position = "none")

a
```


### Top Europe sales of games 
#### In Europe region, Wii Sports and GTA 5 are most sold games. 
```{r, warning = FALSE,echo = FALSE}
top_eusales = aggregate(list(EU_Sales = data$EU_Sales),list(Name = data$Name),FUN = sum)
top_eusales = top_eusales[order(top_eusales$EU_Sales,decreasing = TRUE),]
top_eusales = head(top_eusales,10)
top_eusales

b = ggplot(data = top_eusales, mapping = aes(x = Name, y = EU_Sales)) +
  geom_bar(stat = "identity", mapping = aes(fill = Name, color = Name), size = 1.1, alpha = .7) +
  geom_label(mapping = aes(label = EU_Sales), size = 4) +
  xlab("") +
  ylab("Sales in Europe (in millions)") +
  ggtitle("The 10 best selling games in Europe")+
  scale_x_discrete(guide = guide_axis(n.dodge=2))+
  theme(legend.position = "none")
b
```


### Top Japan Sales of games
#### Pokemon Red is the most sold game in Japan.
```{r, warning = FALSE,echo = FALSE}
top_jpsales = aggregate(list(JP_sales = data$JP_Sales),list(Name = data$Name),FUN = sum)
top_jpsales = top_jpsales[order(top_jpsales$JP_sales,decreasing = TRUE),]
top_jpsales = head(top_jpsales,10)
top_jpsales

c = ggplot(data = top_jpsales, mapping = aes(x = Name, y = JP_sales)) +
  geom_bar(stat = "identity", mapping = aes(fill = Name, color = Name), size = 1.1, alpha = .7) +
  geom_label(mapping = aes(label = JP_sales), size = 4) +
  xlab("") +
  ylab("Sales in Japan (in millions)") +
  ggtitle("The 10 best selling games in Japan")+
  scale_x_discrete(guide = guide_axis(n.dodge=3))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

c
```


### Other Countires Sales
#### GTA 5 is the most played game in other countires.
```{r, warning = FALSE,echo = FALSE}
top_othersales = aggregate(list(Other_Sales = data$Other_Sales),list(Name = data$Name),FUN = sum)
top_othersales = top_othersales[order(top_othersales$Other_Sales,decreasing = TRUE),]
top_othersales = head(top_othersales,10)
top_othersales

d = ggplot(data = top_othersales, mapping = aes(x = Name, y = Other_Sales)) +
  geom_bar(stat = "identity", mapping = aes(fill = Name), size = 1.1, alpha =.7) +
  geom_label(mapping = aes(label = Other_Sales), size = 4) +
  xlab("") +
  ylab("Sales in the in other countries (in millions)") +
  ggtitle("The 10 best selling games in other countries")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_fill_discrete(name = "Games")

d
```


### Top Global Sales of games 
#### Wii Sports is the most played game globally by people
```{r, warning = FALSE,echo = FALSE}
top_globalsales = aggregate(list(Global_sales = data$Global_Sales),list(Name = data$Name),FUN = sum)
top_globalsales = top_globalsales[order(top_globalsales$Global_sales,decreasing = TRUE),]
top_globalsales = head(top_globalsales,10)
top_globalsales

e = ggplot(data = top_globalsales, mapping = aes(x = Name, y = Global_sales)) +
  geom_bar(stat = "identity", mapping = aes(fill = Name), size = 1.1, alpha =.7) +
  geom_label(mapping = aes(label = Global_sales), size = 4) +
  xlab("") +
  ylab("Sales in all over the world (in millions)") +
  ggtitle("The 10 best selling games in all over the world")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_fill_discrete(name = "Games")

e
```
```{r, warning = FALSE,echo = FALSE}
h = ggplot(data = top_globalsales, mapping = aes(x = Name, y = Global_sales)) +
  geom_bar(stat = "identity", mapping = aes(fill = Name, color = Name), size = 0.4, alpha = .7) +
  geom_label(mapping = aes(label = Global_sales), size = 2.8) +
  coord_flip()+
  xlab("") +
  ylab("Sales in the rest of the world (in millions)") +
  ggtitle("The 10 best selling games in rest of the world")+
  theme(legend.position = "none")

h
```

```{r, warning = FALSE,echo = FALSE}

f = ggplot(data = head(top_globalsales,5), mapping = aes(x = Name, y = Global_sales)) +
  geom_line(group = 1) +
  geom_point(mapping = aes(fill = Name),size = 3)+
  xlab("") +
  ylab("Sales in the rest of the world (in millions)") +
  ggtitle("The 10 best selling games in rest of the world")+
  theme(legend.position = "none")

f
```
```{r, warning = FALSE,echo = FALSE}
df_top5 = data[(data$Name == "Wii Sports" | data$Name == "Grand Theft Auto V" | 
                 data$Name == "Super Mario Bros." | data$Name == "Tetris" | data$Name == "Mario Kart Wii"),]
ggplot(data = df_top5, mapping = aes(x = Year,y = Global_Sales))+
  geom_bar(stat = "identity",mapping = aes(color = Name,fill = Name),alpha = 0.7,size = 1)+
  labs(x = "Top 5 games",y = "Sales",title = "Sales of top 5 games over the world")+
  theme(legend.position = "none",axis.text=element_text(size=6.5))+
  facet_wrap(~Name)

```


## Number of Sales per platform

### North America sales
```{r, warning = FALSE,echo = FALSE}
top_nasales = aggregate(list(NA_sales = data$NA_Sales),list(Platform = data$Platform),FUN = sum)
top_nasales = top_nasales[order(top_nasales$NA_sales,decreasing = TRUE),]
datatable(top_nasales)

```
### PS2 and Xbox360 is the most used gaming device by people.
```{r, warning = FALSE,echo = FALSE}
h = ggplot(data = top_nasales,mapping = aes(x = Platform,y = NA_sales))+
  geom_line(group = 1,linetype = "dashed",size = 0.5,color = "purple")+
  geom_label(mapping = aes(label = NA_sales,fill = Platform),size = 2)+
  theme(legend.position = "none",axis.text=element_text(size=6))

h
```

### Europe sales
```{r, warning = FALSE,echo = FALSE}
top_eusales = aggregate(list(EU_Sales = data$EU_Sales),list(Platform = data$Platform),FUN = sum)
top_eusales = top_eusales[order(top_eusales$EU_Sales,decreasing = TRUE),]
datatable(top_eusales)
```
### PS3 and PS2 are most used gaming devices in Europe.
```{r, warning = FALSE,echo = FALSE}
e = ggplot(data = top_eusales,mapping = aes(x = Platform,y = EU_Sales))+
  geom_line(group = 1,linetype = "dashed",size = 0.5,color = "purple")+
  geom_label(mapping = aes(label = EU_Sales,fill = Platform),size = 2)+
  theme(legend.position = "none",axis.text=element_text(size=6))

e
```


### Japan Sales
```{r, warning = FALSE,echo = FALSE}

top_jpsales = aggregate(list(JP_sales = data$JP_Sales),list(Platform = data$Platform),FUN = sum)
top_jpsales = top_jpsales[order(top_jpsales$JP_sales,decreasing = TRUE),]
datatable(top_jpsales)

```
#### Dual Screen is most used gaming device in Japan.
```{r, warning = FALSE,echo = FALSE}
y = ggplot(data = top_jpsales,mapping = aes(x = Platform,y = JP_sales))+
  geom_line(group = 1,linetype = "dashed",size = 0.5,color = "purple")+
  geom_label(mapping = aes(label = JP_sales,fill = Platform),size = 2)+
  theme(legend.position = "none",axis.text=element_text(size=6))
y
```


### Other Countires Sales
```{r, warning = FALSE,echo = FALSE}

top_othersales = aggregate(list(Other_Sales = data$Other_Sales),list(Platform = data$Platform),FUN = sum)
top_othersales = top_othersales[order(top_othersales$Other_Sales,decreasing = TRUE),]
datatable(top_othersales)
```
#### PS2 is most used gaming device in rest of th world.
```{r, warning = FALSE,echo = FALSE}
s = ggplot(data = top_othersales,mapping = aes(x = Platform,y = Other_Sales))+
  geom_line(group = 1,linetype = "dashed",size = 0.5,color = "purple")+
  geom_label(mapping = aes(label = Other_Sales,fill = Platform),size = 2)+
  theme(legend.position = "none",axis.text=element_text(size=6))
s
```
### Global Sales
#### PS2 is the most used gaming device globally.
```{r, warning = FALSE,echo = FALSE}
top_globalsales = aggregate(list(Global_sales =data$Global_Sales),list(Platform = data$Platform),sum)
top_globalsales = top_globalsales[order(top_globalsales$Global_sales,decreasing = TRUE),]
top_globalsales = head(top_globalsales,10)

ggplot(data = top_globalsales,mapping = aes(x = Platform,y = Global_sales))+
  geom_segment(mapping = aes(xend = Platform,yend = 0,color = Platform),size = 1.5)+
  geom_line(group = 1,linetype = "dashed",size = 0.7,color = "black")+
  theme(legend.position = "none")+
  geom_point(mapping = aes(fill = Platform,color = Platform),size = 4)

```
### Total Global Sales by Year
```{r, warning = FALSE,echo = FALSE}
data_global = aggregate(list(Global_Sales = data$Global_Sales),list(Year = data$Year),FUN = sum)

data_global = data_global[order(data_global$Year),]
datatable(data_global)

```
```{r, warning = FALSE,echo = FALSE}
a = ggplot(data = data_global,mapping = aes(x = Year,y = Global_Sales))+
  geom_line(group = 1,linetype = "dashed",color = "blue")+
  geom_point(mapping = aes(color = Year),size = 2,alpha = 0.7)+
  theme(legend.position = "none",axis.text=element_text(size=5.159))

c = ggplot(data = data_global,mapping = aes(x = Year,y = Global_Sales))+
  geom_line(group = 1,color = "blue",size = 1)+
  geom_label(mapping = aes(label = Global_Sales),size = 2,fill = "#88ace0")+
  theme(legend.position = "none",axis.text=element_text(size=5.159))

plot_grid(a,c,nrow = 2,ncol = 1)
```
### We can conclude that, from 2007 to 2010 sales of games over the world was strong.



























